Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}

### 2021-01-01 colt-21/cvx-flats.tex
Tweaking infinite Y proof

\section{Extensions to infinite $\Y$}
\begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
	Let a property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
	Let $L \in \L_d$ be a convex loss\footnote{$\E_p L(u,Y)$ must be a $\A$-convex normal integrand for all $p \in P$} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$ and $p \in \P$.
	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
\end{theorem}
\begin{proof}
	Consider the probability space $(\Y, \A, p)$ so that $\E_p L(u,Y) = \int L(u,y) d(py)$ is well-defined and finite for all $u \in \reals^d$, and $p \in \P$.
	Moreover, let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of properties, there is some $u \in \Gamma(p)$. \jessie{Address if we get rid of minnability}

	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ by indirect elicitation if $u = \psi(r)$. \jessie{though this needs more detail since we don't necessarily have $u = \psi(r)$.}.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$, which is defined to be $ \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \simplex : \int \nu(y) d(py) = 0\}$.

@@

	Moreover, we have that $\codim(F) = \dim(\P \setminus F) = \dim(P) - \dim(F) \leq d$.
	To see this, observe $\dim(\P) \leq d + \dim(F)$.
	As $\dim(\nu) \leq d$ and $F$ is the restriction of $\nu$ to $p \in \P$, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
	\jessie{This is pretty fuzzy to me, but hopefully the edit distance is small.}
	\jessie{\url{https://www.youtube.com/watch?v=2Q_ZzBGPdqE}}

	\bigskip

	Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
	Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
	If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.

	Now if $|\gamma(p)| > 1$ there are two cases.
	If $r = \psi(u)$, we are trivially done.
	If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}

\end{proof}

>>>>

\section{Extensions to infinite $\Y$}
\begin{theorem}[Theorem ~\ref{thm:cvx-flats} with infinite $\Y$]
	Let a single-valued property $\gamma : \P \toto \R$ be given, and let $p \in \P$, and $r \in \gamma(p)$.
	Let $L \in \L_d$ be a convex loss\footnote{$\E_p L(u,Y)$ must be a $\A$-convex normal integrand for all $p \in P$} such that such that $\E_p L(\cdot,Y)$ is finite for all $u \in \reals^d$ and $p \in \P$.
	If $L$ indirectly elicits $\gamma$, there is a flat $F$ with $p \in F \cap \P \subseteq \gamma_r$ with $\codim(F) \leq d$.
\end{theorem}
\begin{proof}
	Consider the probability space $(\Y, \A, p)$ so that $\E_p L(u,Y) = \int L(u,y) d(py)$ is well-defined and finite for all $u \in \reals^d$, and $p \in \P$.
	Moreover, let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$.
	By definition of properties, there is some $u \in \Gamma(p)$. \jessie{Address if we get rid of minnability}

	We first construct the flat $F$ and show $F \cap \P \subseteq \Gamma_u$, which implies $F \cap \P \subseteq \gamma_r$ since we must have $u = \psi(r)$ by indirect elicitation and $\gamma$ being single-valued.

	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \E_p L(u,Y)$.
	Since, for each $p \in \P$, we have $L$ satisfying the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\vec 0 \in \partial \E_p L(u,Y) \iff \vec 0 \in \E_p \partial L(u,Y)$, which is defined to be $ \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.
	As $\vec 0$ is in the expectation of the subgradient, such a $\nu$ exists, so we take $F := \ker(\nu) \cap \P$, where $\ker(\nu) := \{p \in \P : \int \nu(y) d(py) = 0\}$.

@@

	Moreover, we want to show that $\codim(F) = \dim(\P \setminus F) = \dim(\P) - \dim(F) \leq d$.
	%To see this, observe $\dim(\P) \leq d + \dim(F)$.
	As $\dim(\nu) \leq d$ (by construction, as it is a subgradient of a $d$-dimensional loss), we must have $\dim(\ker(\nu)) \geq \dim(\P) - d$.
	Thus, we have $\dim(F) = \dim(\P \cap \ker(\nu) ) \geq \dim(\P) - d$, giving the desired result.
	\jessie{This is pretty fuzzy to me, but hopefully the edit distance is small.}
	\jessie{\url{https://www.youtube.com/watch?v=2Q_ZzBGPdqE}}
%	
%
%	\bigskip
%	
	%Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
	%Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
	%If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
	%Now if $|\gamma(p)| > 1$ there are two cases.
	%If $r = \psi(u)$, we are trivially done.
	%If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}	
\end{proof}
